### 2021-06-28 README.Rmd
added addNA and changevar, and ability to alter starting year of projection at will. No EWN

* 2021-06-24 aMSE 0.0.0.2100 Big jump in number as some larger changes. I have removed a bunch of deprecated functions (which are now in 'deprecated.R' in the data-raw directory). I have tidied many other functions, and have modified listall files to aid in the auto-documentation of the package.

@@

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# run the scenario ----------------------------------------------------
#source(paste0(ddir,"aMSEUse/scenarios/MSE_Source.R"))
out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,
              hcrfun=mcdahcr,sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
              getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=32,
              cleanslate=TRUE,verbose=TRUE,doproject=TRUE,ndiagprojs=3)
# make results webpage ---------------------------------------------------------
replist <- list(starttime=as.character(out$starttime),
                endtime=as.character(out$projtime))
glb <- out$glb
runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
                   "  replicates = ",glb$reps,",   years projected = ",glb$pyrs,
                   "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
                   "  Randomseed for conditioning = ",out$ctrl$randseed)

# Unhash the make_html command to generate the results webspage
# make_html(
#   replist = replist,
#   rundir = rundir,
#   width = 500,
#   openfile = TRUE,
#   runnotes = NULL,
#   verbose = FALSE,
#   packagename = "aMSE",
#   htmlname = "hs652510"
# )

@@

```{r }
str(out$zoneDP,max.level=1)

>>>>

* 2021-06-28 aMSE 0.0.0.2000 The AMSE can now conduct what are effectively retrospective analyses. This is affected by changing the 'CATCHES, 47, if>1 this is the number of historical catch years' line in the control.csv file, which can now be done in a loop using the new 'changevar' function. This has necessitated also changing the 'CEYRS, 20, The first year of catches for which there are CPUE records, ie 1992 is 20th year of catches', which used to take a direct value of how any years of CPUE data there are. We could have just changed two numbers but along that path errors lay.

@@

# TasmanianHS.R should be in rundir, but during development is in data-raw
source(paste0(datadir,"/TasmanianHS.R"))
controlfile <- "controlsau.csv"
# run the scenario --------------------- Obviously unhash this to make it work
#out <- do_MSE(rundir,controlfile,datadir,hsargs=hsargs,
#              hcrfun=mcdahcr,sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
#              getdata=tasdata,calcpopC=calcexpectpopC,varyrs=7,startyr=32,
#              cleanslate=TRUE,verbose=TRUE,doproject=TRUE,ndiagprojs=3)
# make results webpage ---------------------------------------------------------
# replist <- list(starttime=as.character(out$starttime),
#                 endtime=as.character(out$projtime))
# glb <- out$glb
# runnotes <- paste0(out$ctrl$runlabel,":  RunTime = ",out$tottime,
#                    "  replicates = ",glb$reps,",   years projected = ",glb$pyrs,
#                    "  Populations = ",glb$numpop," and SAU = ",glb$nSAU,
#                    "  Randomseed for conditioning = ",out$ctrl$randseed)
# Unhash the make_html command to generate the results webspage
# make_html(
#   replist = replist,
#   rundir = rundir,
#   width = 500,
#   openfile = TRUE,
#   runnotes = NULL,
#   verbose = FALSE,
#   packagename = "aMSE",
#   htmlname = "hs652510"
# )

@@

```{r }
#str(out$zoneDP,max.level=1)
